### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Evaluation}
In this section, we evaluate \tool{} on several small benchmarks and real-world software trying to answer the following questions:

\begin{itemize}
\item \textbf{Effectiveness:} Can \tool{} quantify the information leakage with an conservative estimation? If so, what is loss compared it with the real leakage?
\item \textbf{Performance:} How much overhead can \tool{} produce?
\item \textbf{Usage:} What is the real usage of \tool{}? Can \tool{} handle both Cryptography and Non-cryptography libraries? Can \tool{} help developers find and fix side-channel leakages?
\end{itemize}

@@

\begin{sidewaystable}
\footnotesize
\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{chapter5:table:over_result}
\begin{tabular}{lrrrrrrrrrrrr}\toprule

>>>>

\section{Evaluation}
In this section, we evaluate \ctool{} on several small benchmarks and real-world software trying to answer the following questions:

\begin{itemize}
\item \textbf{Effectiveness:} Can \ctool{} quantify the information leakage with an conservative estimation? If so, what is the loss compared it with the real leakage?
\item \textbf{Performance:} How much overhead can \ctool{} produce?
\item \textbf{Usage:} What is the real usage of \ctool{}? Can \ctool{} handle both Cryptography and Non-cryptography libraries? Can \ctool{} help developers find and fix side-channel leakages?
\end{itemize}

@@

\begin{sidewaystable}
\footnotesize
\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{chapter5:table:over_result}
\centering
\begin{tabular}{lrrrrrrrrrrrr}\toprule
